SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-02-24 scipy-1.0/paper.tex
removed inappropriate colons http://www.kentlaw.edu/academics/lrw/grinker/LwtaColons.htm
fixed incomplete sentence... and got carried away

For implementing new functionality, we have a clear order of language
preference.  First Python, if performance is not an issue. If it is, then in
order of preference: Cython, C, C++, Fortran. The main motivation for this is
maintainability: Cython has the highest abstraction level and most Python
developers will understand it. C is also widely known, and easier to deal with
for the core development team than C++ and especially Fortran.

>>>>

For implementing new functionality, Python is the first choice. If Python performance is an issue, then 
we use Cython, C, C++, or Fortran (listed in order of preference). The main motivation for this is
maintainability: Cython has the highest abstraction level and most Python
developers will understand it. C is also widely known, and easier to deal with
for the core development team than C++ and especially Fortran.
